---
title: "route-graph"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{route-graph}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error=TRUE,
  out.width = "\\textwidth",
  fig.height = 8,
  fig.width = 8
)
```

```{r setup, message=FALSE}
library(supermetroid)
library(tidyverse)
library(ggraph)
library(tidygraph)

```

## Route graph

Create a digraph to represent all routes taken by players.

## extract bits I need

```{r}
long_routes <- 
  sio_df %>% 
  select(run_id, supermetroid_label, realtime_end_ms, realtime_start_ms)

head(long_routes)


```

```{r}
# take a look at a dataset from ggraph
highschool %>% head()

```

Need to use `realtime_start_ms` and `realtime_end_ms` to figure out which one is from and to? Hmmm, or just use itself.

```{r}
# take a look at one run
run_events <- 
long_routes  %>% 
  filter(run_id == last(run_id),
         !is.na(supermetroid_label)) %>% 
  arrange(realtime_start_ms) %>% 
  pull(supermetroid_label)

# and create a from, to df
tibble(
  from = c("start", run_events),
  to = c(run_events, "end")
)


```

## Create a from-to dataframe for each route

```{r}
route_from_to_df <- function(this_route, this_route_id) {
  route_events <- this_route$supermetroid_label
  
  # and create a from, to df
  tibble(from = c("start", route_events),
         to = c(route_events, "end"))
}

route_from_to_df(distinct_routes$route[[3]], distinct_routes$route_id[[3]])

# now can apply to df
from_to_df <-
  distinct_routes %>%
  mutate(
    runs = map_int(run_id, nrow),
    from_to = map2(route, route_id, route_from_to_df)
  ) %>%
  select(from_to, route_id, runs) %>%
  unnest(from_to)

head(from_to_df)
```



```{r, eval=FALSE}

usethis::use_data(from_to_df)


```



## Create a digraphs that describe what routes players take

```{r}
from_to_gg <- 
  from_to_df %>% 
  as_tbl_graph()

```

### Too messy

```{r}
from_to_gg %>% 
  ggraph() +
  geom_edge_fan(aes(size = runs))
  

```

### Need order


```{r}
from_to_gg %>%
  ggraph(layout = "linear", circular = TRUE) +
  geom_edge_fan(aes(size = runs), alpha = 0.2) +
  geom_node_point(aes(colour = ))


```


### Need direction


```{r}
from_to_gg %>%
  ggraph(layout = "linear") +
  geom_edge_fan(aes(size = runs), alpha = 0.2) +
  geom_node_point()


```



### Too many nodes for EDA

```{r}
from_to_gg %>% 
  ggraph(layout = "linear") +
  geom_edge_arc(arrow = arrow(), aes(alpha = runs)) 


```

## Strats

Discussed with  `@anatomecha` which game events are most important to gamer strategies he is interested in, *strats*.

```{r}
bosses <- c("kraid", "phantoon", "draygon", "ridley")
loot <- c("ice beam", "grapple beam")


selected_splits <- c("kraid","ice beam", "gravity suit", "draygon", "ridley", "varia suit", "space jump")

```

```{r}



```

```{r}



```


