---
title: "sio"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sio}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=FALSE
)
```

```{r setup}
library(supermetroid)
```

```{python}
import pandas as pd
import splitsio
```


# splits.io data

## Load runs and runners  

```{python eval=FALSE}
# this chunk is not evaluated 
# to minimise api calls

# get 100% Category Super Metroid game data  
sio_cat = splitsio.Category.from_id("279", historic=False)
save_object(sio_cat, "data-raw/sio_cat.pkl")

```


```{python load splitsio dat}
# load sio data
with open('data-raw/sio_cat.pkl', 'rb') as inp:
    sio_cat = pickle.load(inp)

# extract runners and run from category
sio_runners = sio_cat.runners()

sio_runs = sio_cat.runs()



```


# Try with converting to a dictionary much earlier


```{python}
type(sio_runs)
sio_runs.__dict__.keys()

sio_runs.__dict__.keys()

```


```{python}
sio_run_dict_max = 3

sio_run_dicts = [sio_runs[x].to_dict() for x in range(sio_run_dict_max)]

# each element of the list is a dictionary with keys
sio_run_dicts[0].keys()

```

```{r}
testing_index <- 3

# find 

```


## Inspect data


```{python}
# take a look at a run
sio_runs[0]

# can we call nested elements by index and key?
type(sio_runs[0])
# I think this is a series object?
print(pd.DataFrame(sio_runs[1:3]))

print(pd.DataFrame(sio_runs[1:3]).columns)

```


```{python }
# take a look at a runner
sio_runners[0]

```

## Run dataframe

Objective: to wrangle a data frame with run data

sio_run_df | description | splitsio 
- | - | - 
*run_id* | splits.io id | `id` | 
date | timestamp of run upload | ? `'created_at', 'parsed_at', 'updated_at'` we'll use 'updated_at' for now, but should check splitsio docs for which
run_time | total time of run in s or ms | `realtime_duration_ms`
rank | "historical" if from previous record (nb only applies to speedrun.com); otherwise rank as int, list column | ?
src_player_id | speedrun.com player id | `srdc_id`

## Try with list of dictionaries

```{python}
sio_run_dicts = [sio_runs[x].to_dict() for x in range(len(sio_runs))]

# each element is a dictionary with keys
sio_run_dicts[0].keys()

```

```{python}
# run id
sio_run_dicts[0].keys()

# get id
sio_run_dicts[0]['id']

# get realtime
sio_run_dicts[0]['realtime_duration_ms']

```

```{python}
# player data
pd.json_normalize(sio_run_dicts[0]['runners'])['id'][0]

sio_run_player_index = 10 # len(sio_run_dicts)

run_runners_list = [pd.json_normalize(sio_run_dicts[x]['runners']).assign(run_id = sio_runs[x].id) for x in range(len(sio_runs))]

run_runners_concat = pd.concat(run_runners)

run_runners = run_runners_concat[['display_name', 'name', 'run_id','id']].rename(columns={'id':'player_id', 'name':'player_name'})

len(run_runners) != len(sio_runs) # :( whyeee

sio_run_dicts[0].keys()

sio_runs_df = pd.DataFrame({
  'run_id' : [sio_run_dicts[x]['id'] for x in range(len(sio_runs))],
  't_ms' : [sio_run_dicts[x]['realtime_duration_ms'] for x in range(len(sio_runs))],
  'date' : [sio_run_dicts[x]['updated_at'] for x in range(len(sio_runs))],
  'image_url': [sio_run_dicts[x]['image_url'] for x in range(len(sio_runs))],
  'video_url': [sio_run_dicts[x]['video_url'] for x in range(len(sio_runs))]
}).merge(run_runners, on = "run_id", how = 'left').set_index('run_id')

# get segments



```



```{r}
inspect_sio_runs <- py$sio_runs_df %>% select(-contains("url")) %>% 
  select(display_name, everything())

```



## create segments dataframe

segment_df | description
- | - 
*run_id* | unique identifier of run
segment_id | unique identifier of segment
t_s | time in seconds, measured to millisecond precision

```{python}
# first level of segments
type(sio_df['segments'][0])
len(sio_df['segments'][0])

# second level of segments
type(sio_df['segments'][0][0])
sio_df['segments'][0][2].keys()


segments_list = [pd.DataFrame(sio_df.segments[x]).assign(run_id = sio_df.id[x]) for x in range(sio_df.shape[0]) ]

segment_raw = pd.concat(segments_list)

segment_raw.columns
segment_raw.shape

sio_segments_df = segment_raw.merge(
  sio_runs_df[['player_name', 'player_id']], on = "run_id", how="left")


```

```{r}
# tidy it up in R before writing it

sio_segments <- py$sio_segments_df


sio_splits_df <- 
sio_segments %>% 
  select(
    player_name, 
    game_event = display_name, 
    segment_number, 
    realtime_start_ms, 
    segment_id = id,
    run_id,
    player_id,
    everything()) %>% 
  select(-contains("gametime"),
         -contains("reduced"),
         -contains("skipped"), -histories) %>% 
  mutate(
    player_id = as.character(player_id))

```

```{r eval=FALSE}
usethis::use_data(sio_splits_df)

```
