---
title: "sio"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sio}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error=TRUE
)
```

```{r setup, message=FALSE}
library(supermetroid)
library(tidyverse)
library(reticulate)
```

```{python}
import pandas as pd
import splitsio
import json

# try to fix the issue in src, possibly ask Anthony
```


# splits.io data

## Load runs and runners  

This module has its own types; here I convert to a list of dictionaries I can 
save locally so I don't have to call the API every time I knit the html. 


```{python, eval=FALSE}
# this chunk is not evaluated 
# to minimise api calls

# get 100% Category Super Metroid game data  
sio_cat = splitsio.Category.from_id("279", historic=True)
type(sio_cat)
# extract runners from category  
sio_runners = sio_cat.runners()
type(sio_runners)
sio_runners[0]
sio_runners[-1]

# extract run from category
sio_runs = sio_cat.runs()
type(sio_runs)
sio_runs[0]
sio_runs[-1]


# convert the run objects to dictionaries
sio_run_dicts = [sio_runs[x].to_dict() for x in range(len(sio_runs))]

# each element is a dictionary with keys
sio_run_dicts[0].keys()


# run id
sio_run_dicts[0].keys()

# get id
sio_run_dicts[0]['id']

# get realtime
sio_run_dicts[0]['realtime_duration_ms']

print(sio_run_dicts)
import pprint
pp = pprint.PrettyPrinter(indent=4)
pp.pprint(sio_run_dicts[0:3])
sio_cat.__dict__
for key in sio_cat.keys():
  print(key.__dict__)

# save object locally
file_path = "data-raw/sio_cat.json"
with open(file_path, "w") as outfile:
  outfile.write(json.dumps(sio_run_dicts, indent=4))


```

## Run dataframe

Objective: to wrangle a data frame with run data

sio_run_df | description | splitsio 
- | - | - 
*run_id* | splits.io id | `id` | 
date | timestamp of run upload | ? `'created_at', 'parsed_at', 'updated_at'` we'll use 'updated_at' for now, but should check splitsio docs for which
run_time | total time of run in s or ms | `realtime_duration_ms`
rank | "historical" if from previous record (nb only applies to speedrun.com); otherwise rank as int, list column | ?
src_player_id | speedrun.com player id | `srdc_id`

## Try with list of dictionaries

```{python eval=FALSE, echo=FALSE}
with open("data-raw/sio_cat.json", "r") as infile:
  sio_run_dicts = json.load(infile)


```


```{python}
with open("../data-raw/sio_cat.json", "r") as infile:
  sio_run_dicts = json.load(infile)


```

```{python}
# player data
pd.json_normalize(sio_run_dicts[0]['runners'])['id'][0]

sio_run_player_index = 10 # len(sio_run_dicts)

run_runners_list = [pd.json_normalize(sio_run_dicts[x]['runners']).assign(run_id = sio_run_dicts[x]['id']) for x in range(len(sio_run_dicts))]

run_runners_concat = pd.concat(run_runners_list)

run_runners = run_runners_concat[['name', 'run_id','id']].rename(columns={'id':'player_id', 'name':'player_name'})

sio_run_dicts[0].keys()

```

```{python}
# create a dataframe

sio_runs_df = pd.DataFrame({
  'run_id' : [sio_run_dicts[x]['id'] for x in range(len(sio_run_dicts))],
  't_ms' : [sio_run_dicts[x]['realtime_duration_ms'] for x in range(len(sio_run_dicts))],
  'date' : [sio_run_dicts[x]['updated_at'] for x in range(len(sio_run_dicts))],
  'image_url': [sio_run_dicts[x]['image_url'] for x in range(len(sio_run_dicts))],
  'video_url': [sio_run_dicts[x]['video_url'] for x in range(len(sio_run_dicts))]
})


sio_runs_df.head()


```

```{python }
# need to merge with run runners
run_runners.head()

run_runners_df = sio_runs_df.merge(
  run_runners, on = "run_id", how = 'left').reset_index(drop=True)

# run and runner data
run_runners_df.head()

```

## create segments dataframe

segment_df | description
- | - 
*run_id* | unique identifier of run
segment_id | unique identifier of segment
game_event | description of split 
t_s | time in seconds, measured to millisecond precision

```{python}
# first level of segments
type(sio_run_dicts[0]['segments'])
type(sio_run_dicts[0]['segments'][0])

# inspect a segment
sio_run_dicts[0]['segments']

# a single segment
sio_run_dicts[0]['segments'][0].keys()

# convert to df
# I think this is a dictionary of single-element entries, so can be flattened
# how to efficiently check this?
pd.DataFrame(sio_run_dicts[0]['segments']).head()

# List of dataframes of segments for each run
segments_list = [pd.DataFrame(sio_run_dicts[x]['segments']).assign(run_id = sio_run_dicts[x]['id']) for x in range(len(sio_run_dicts))]

segment_raw = pd.concat(segments_list).reset_index(drop=True)

segment_raw.columns
segment_raw.shape
segment_raw.head()


```

```{python}

segment_raw.columns
sio_runs_df.columns

# sio_segments_df = (segment_raw.rename(
#   {
#     'display_name': 'player_name'
# }
# ).merge(
#   sio_runs_df, on = "run_id", how="left"))

sio_segments_df.shape
sio_segments_df.columns
sio_segments_df.head()


```


```{r}
# tidy it up in R before writing it

sio_segments <- py$segment_raw
sio_runs <- py$run_runners

sio_seg_runs <- left_join(sio_segments %>% distinct(), 
                          sio_runs %>% distinct() %>% 
                            rename(total_t_ms = t_ms) %>% 
                            select(-video_url, -image_url, -date)
                            , by = "run_id")

colnames(sio_seg_runs)

sio_seg_runs %>% 
  count(run_id, id) %>% 
  arrange(desc(n)) %>% 
  filter(n > 1) 

sio_splits_df <- 
  sio_segments %>% 
    select(
      player_name = name, 
      game_event = display_name, 
      segment_number, 
      realtime_start_ms, 
      segment_id = id,
      run_id,
      player_id,
      everything()) %>% 
    select(-contains("gametime"),
           -contains("reduced"),
           -contains("skipped"), -histories) %>% 
    mutate(player_id = as.character(player_id)))

head(sio_splits_df)

```

```{r eval=FALSE}
# write data - this chunk is not evaluated on knit
usethis::use_data(sio_splits_df, overwrite = TRUE)

```
