---
title: "splits"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{splits}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  error=TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 8,
  fig.align = 'center'
)
```

```{r setup, message=FALSE}
library(supermetroid)
library(tidyverse)
library(gt)

```

## This document updates splitsio df for the analysis

## Get segment labels

Splits, or segments, measure at what time a game event happens, and how long a player took to get there from their previous segment. 

### Unique split id?

Although segments are chosen by a program, so far we've only found the player labels for each split or segment. Players can define their own segments and labels, too, so we don't want to confuse those points with others. 

On the other hand we don't want to keep `bomb` and throw out all the `bombs` with the bathwater. 

```{r}
labels_dat <- 
  # pull columns for this analysis from splits data
  sio_splits_df %>% 
  select(player_name, game_event, name, segment_number, run_id, player_id) %>% 
  mutate(
    # create a lower-case label 
    label = tolower(game_event)
    )
labels_dat %>% head()

```


## Most common labels

```{r}
label_counts <- 
labels_dat %>% 
  mutate(
    starts_with = str_sub(label, 1, 1)
  ) %>% 
  count(starts_with, label) %>% 
  arrange(starts_with, desc(n))

```

```{r}
label_counts %>% 
  ungroup() %>% 
  select(-starts_with) %>%  
  arrange(desc(n)) %>% 
  head(30) %>% 
  gt()

```


```{r eval=FALSE}

# write labels to sheet for labelling 
# https://docs.google.com/spreadsheets/d/1FRHsS7WQvVhI5_yP-twHCJW2YRJRbeKg4P42EY3Jzrk/edit#gid=1079532092


write_csv(label_counts, "data-raw/sio-label-counts.csv")

relabels <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1FRHsS7WQvVhI5_yP-twHCJW2YRJRbeKg4P42EY3Jzrk/edit#gid=1079532092")

write_csv(relabels, "data-raw/sio-relabels.csv")

```

## Add labels

```{r}
relabels <- read_csv("data-raw/sio-relabels.csv") %>% 
  select(label, supermetroid_label) %>% 
  distinct()

```

```{r}

sio_relabelled <- 
sio_splits_df %>% 
  mutate(
    label = tolower(game_event)
  ) %>% 
  left_join(relabels, by = "label")


```



```{r}
# check out counts now
sio_relabelled %>% 
  ungroup() %>% 
  count(supermetroid_label) %>% 
  arrange(desc(n)) %>% 
  head(30) %>% 
  gt()

```

```{r}
sio_df <- sio_relabelled %>% 
  select(-name) %>% 
  select(supermetroid_label, everything(), split_player = label)

sio_df %>% head()

```

```{r eval=FALSE}
usethis::use_data(sio_df)

```


## What routes do people take?

```{r}
routes_raw <- 
sio_df %>% 
  select(supermetroid_label, player_name, split_order = segment_number, realtime_end_ms, run_id, player_id) %>% 
  # get just the universal splits
  filter(!is.na(supermetroid_label))


```


```{r}
splits_orders <- 
routes_raw %>% 
  select(supermetroid_label, split_order, run_id)

nested_splits <- 
splits_orders %>% 
  arrange(run_id, split_order) %>% 
  select(-split_order) %>% 
  group_by(run_id) %>% 
  nest(splits = supermetroid_label) %>% 
  ungroup() %>% 
  group_by(splits) %>% 
  nest(runs = run_id) %>% 
  ungroup() %>% 
  mutate(
    route_length = map_int(splits, nrow),
    route_id = str_c("route ", 1:n())
  ) %>% 
  arrange(desc(route_length))
  
nested_splits %>%
  head() %>% 
  gt()

```



```{r}
anatomecha_splits <-
  # get standard order
  sio_df %>%
  filter(player_name == "anatomecha",!is.na(supermetroid_label)) %>%
  arrange(segment_number) %>%
  # should really filter to last date
  # will need to fix this when there's more than one anatomecha run
  select(supermetroid_label) %>%
  mutate(split_anatomecha = 1:n())

levels(sio_df$split) <- anatomecha_splits$split


```

```{r eval=FALSE}

usethis::use_data(anatomecha_splits)

```



```{r}
routes <- 
nested_splits %>%
  # head() %>% 
  mutate(event = map(splits, \(df) left_join(df, anatomecha_splits, by = "supermetroid_label")),
         route_anatomecha = map(event, \(df) df %>% filter(!is.na(split_anatomecha)) %>%  pull(split_anatomecha)),
         route_standard = map_lgl(route_anatomecha,
                                  \(x) all(sort(x) == x))
         )

 

```



## time vs cumulative time by splits


```{r}
# dashboard this for y axis
# dashboard this for x axis, too selector tool with tick boxes, select all, clear

# plot <- 
  sio_df %>% 
  left_join(anatomecha_splits, by = "supermetroid_label") %>% 
  filter(!is.na(supermetroid_label)) %>% 
  mutate(split_anatomecha = as_factor(split_anatomecha),
         t_h = realtime_end_ms/1000/60
         ) %>% 
  ggplot(aes(x = split_anatomecha, y = t_h, group=run_id)) +
  geom_line(colour=sm_cols$orange, alpha = 0.2) +
  geom_point(colour=sm_cols$orange, alpha = 0.2) +
  theme_sm(base_size = 30) +
  labs(
    title = "Players take different routes",
    subtitle = "Real time completion of each game event would be 
      always increasing if all players took the same route as anatomecha" %>% str_wrap(60),
    x = "Game event (loot, boss, etc.)" %>% str_wrap(12),
    y = "Real time completion (minutes)" %>% str_wrap(20),
    caption = "splits.io"
  ) +
  theme(
    axis.text.x = element_text(angle=90)
  ) +
  scale_x_discrete(labels=c("start", anatomecha_splits$supermetroid_label)) +
  facet_grid(route_standard ~. ) 

# ggplotly(plot)


```

```{r}
# selected_split <- "ice beam" 
selected_split <- "ice beam"# sample(anatomecha_splits$supermetroid_label, 1)
rank <- c(1,25)

#xlim <- c(0.8, 1.2)

# +
#   xlim(xlim[1], xlim[2])



```

# Towards the best route 

## identifying clusters

### Try [knn](https://stats.stackexchange.com/questions/318968/knn-and-k-folding-in-r)

Wide-form array: 
  - columns as events 
  - rows as routes 
  - values as mean event time 

I think this should work on individual observations. 

1. Get an array of segments
2. Set an n-fold cross validation
3. Evaluated the accuracy of the KNn classifer with different values of k by cross validation

```{r}
# get an array of segments
```

```{r}
```



## identifying clusters

Try taking the mean value of each event of each route, then imputing the missing values from local means. How to impute via local mean? That is, need to impute, conditional on the other values in the array. Need to read about imputation. Perhaps I should just write my own imputation, I think I could calculate that. Then apply hierarchical clustering to find out which. 


```{r}
# create wideform array
routes_wide <- 
  routes_raw %>% 
    rename(game_event = supermetroid_label) %>% 
    group_by(run_id) %>% 
    filter(realtime_end_ms == max(realtime_end_ms),
           game_event %in% anatomecha_splits$supermetroid_label
           ) %>% 
    ungroup() %>% 
    distinct() %>% 
    # dplyr::group_by(run_id, game_event) %>%
    # dplyr::summarise(n = dplyr::n(), .groups = "drop") %>%
    # dplyr::filter(n > 1L) 
    pivot_wider(id_cols = "run_id", 
                names_from = "game_event", 
                values_from = "realtime_end_ms") 

  
```


```{r}
library(caret)

trControl <- trainControl(method  = "cv",
                          number  = 5)


fit <- train(supermetroid_label ~ realtime_end_ms,
             method     = "knn",
             tuneGrid   = expand.grid(k = 1:10),
             trControl  = trControl,
             metric     = "Accuracy",
             data       = routes_raw)


```

```{r}
routes_wide <- 
routes %>% 
  select(route_id, runs) %>% 
  unnest(runs) %>% 
  left_join(sio_df %>% 
              filter(split %in% anatomecha_splits$supermetroid_label) %>% 
              select(run_id,
                     realtime_end_ms, split) %>% 
              group_by(run_id, split) %>% 
              filter(realtime_end_ms==max(realtime_end_ms)), 
            by = "run_id") %>% 
  group_by(route_id, run_id) %>% 
  # 0 entries must be corrupt?
  filter(realtime_end_ms != 0) %>% 
  pivot_wider(names_from = "split", values_from = "realtime_end_ms") %>% 
  janitor::clean_names()

```

```{r eval=FALSE}
sio_routes_wide <- routes_wide

usethis::use_data(sio_routes_wide)

```


```{r}




library(caret)

preProcValues <-
  preProcess(routes_wide %>% ungroup() %>% select(-c(run_id, route_id)))

trControl <- trainControl(method  = "cv",
                          number  = 5)

# routes_wide %>% names() %>% paste(collapse ="+") %>%  cat()
fit <-
  train(
    route_id ~ morph_ball + bombs +
      charge_beam + varia_suit + speed_booster +
      wave_beam + grapple_beam + ice_beam + gravity_suit +
      space_jump + spring_ball +
      plasma_beam + screw_attack + spazer +
      hi_jump_boots + phantoon + draygon +
      ridley + kraid + x_ray + mother_brain + escape,
    method     = "knn",
    tuneGrid   = expand.grid(k = 1:10),
    trControl  = trControl,
    metric     = "Accuracy",
    data       = routes_wide
  )


predict(preProcValues)


```


```{r}
ice_beam <- 
routes_wide %>% 
  select(route_id, route_id, ice_beam) %>% 
  group_by(route_id) %>% 
  summarise(
    ice_beam = mean(ice_beam)
  ) %>% 
  ungroup() %>% 
  filter(!is.na(ice_beam)) 

clusters <- dist(ice_beam) %>% hclust()

plot(clusters, labels = ice_beam$route_id)



```

```{r}
library(ggdendro)

ggdendrogram(clusters)

# fuckit write csv
write_csv(routes_wide, "dev/routes_wide.csv")

```


```{python}
import numpy as np
from sklearn.impute import KNNImputer

routes_wide = pd.read_csv("dev/routes_wide.csv")

imputer = KNNImputer()

df_knn_imputed = pd.DataFrame(imputer.fit_transform(routes_wide.drop(columns = ['run_id', 'route_id'])))

```

```{r}
# set up df of imputed data in R
x_event = py$df_knn_imputed

colnames(x_event) <- routes_wide %>% ungroup() %>%  select(-c(route_id, run_id)) %>% colnames()

routes_imputed = 
  routes_wide %>% select(route_id, run_id) %>% bind_cols(x_event)


```


```{r}

# try using caret to do knn classification

routes_imputed %>% View()

routes_scaled <- 
  routes_imputed %>%  
    ungroup() %>% 
    select(-c(route_id, run_id)) %>% 
    mutate(across(everything(), scale)) %>% 
  bind_cols(routes_imputed %>% select(route_id, run_id)) %>% 
  select(route_id, run_id, everything())

# https://rpubs.com/pmtam/knn

# Run algorithms using 10-fold cross validation
trainControl <- trainControl(method="repeatedcv", number=10, repeats=3)
metric <- "Accuracy"

grid <- expand.grid(.k=seq(1,20,by=1))

fit.knn <- train(route_id  # ~ ice_beam,
                 ~ # run_id 
                   + morph_ball + bombs +
      charge_beam + varia_suit + speed_booster +
      wave_beam + grapple_beam + ice_beam + gravity_suit +
      space_jump + spring_ball +
      plasma_beam + screw_attack + spazer +
      hi_jump_boots + phantoon + draygon +
      ridley + kraid + x_ray + mother_brain + escape, 
      data=routes_scaled %>% select(-run_id), method="knn",
                 metric=metric ,trControl=trainControl, tuneGrid=grid)


knn.k1 <- fit.knn$bestTune # keep this Initial k for testing with knn() function in next section
print(fit.knn)


```

